Unlocking Sensitivity for Visibility-based Estimators of the 21\,cm Reionization Power Spectrum

### 2017-07-22 Rotation paper/draft_working.tex
save

One benefit of delay-transform based power-spectrum estimation is the ability to isolate foregrounds in Fourier space. We show that our proposed estimator does not lead to extra foreground leakage into the EoR window. We then apply our estimator to a variety array configurations. We show that for different configurations of PAPER and HERA, the incorporation of partial redundancy accounts for $20\%$ to $60\%$ of the array's total sensitivity. The proposed power-spectrum estimator retains benefits of delay-transform techniques for isolating foregrounds and avoiding systematics and enables one to unlock the full sensitivity of a redundant radio interferometer while simultaneously enjoying the benefits of delay-transform techniques for isolating foregrounds and avoiding systematics.

>>>>

One benefit of delay-transform based power-spectrum estimation is the ability to isolate foregrounds in Fourier space. We show that our proposed estimator does not lead to extra foreground leakage into the EoR window. We then apply our estimator to a variety array configurations. We show that for arrays with increasing number of antennas, partially redundant baselines make up a more significant portion of the array's total sensitivity. The proposed power-spectrum estimator retains benefits of delay-transform techniques for isolating foregrounds and avoiding systematics and enables one to unlock the full sensitivity of a redundant radio interferometer while simultaneously enjoying the benefits of delay-transform techniques for isolating foregrounds and avoiding systematics.
